High-order Solution Transfer between Curved Triangular Meshes

### 2019-06-21 doc/paper.tex
Removed remark about leaving domain.
Based on review feedback. The comment

> if it causes the mesh to leave the domain being analyzed

was too vague and didn't deliver much value. One reviewer interpreted
it as having contradicted the idea of a free boundary. (The original
intent was aimed at problems on an infinite domain with a solution
that dissipates to 0 outside the domain. In these cases, boundary
elements are just there to "box in" the solution.)

Lagrangian methods treat each point in the
physical domain as a ``particle'' which moves along a characteristic curve
over time and then monitor values associated with the particle (heat / energy,
velocity, pressure, density, concentration, etc.). They are an effective way
to solve PDEs, even with higher order or non-linear terms \cite{MR3023731}.
This approach transforms the numerical solution of PDEs into a family of
numerical solutions to many independent ODEs. It allows the use of familiar
and well understood ODE solvers. In addition, Lagrangian methods often
have less restrictive conditions on time steps than Eulerian
methods\footnote{In Eulerian methods, the mesh is fixed.}.
When solving PDEs on unstructured meshes
with Lagrangian methods, the nodes move (since they
are treated like particles) and the mesh ``travels''.
A flow-based change to a mesh can cause problems if it causes the mesh to
leave the domain being analyzed or if it distorts the mesh until the element
quality is too low in some mesh elements. Over enough time, the mesh can
even tangle (i.e. elements begin to overlap).

>>>>

Lagrangian methods treat each point in the
physical domain as a ``particle'' which moves along a characteristic curve
over time and then monitor values associated with the particle (heat / energy,
velocity, pressure, density, concentration, etc.). They are an effective way
to solve PDEs, even with higher order or non-linear terms \cite{MR3023731}.
This approach transforms the numerical solution of PDEs into a family of
numerical solutions to many independent ODEs. It allows the use of familiar
and well understood ODE solvers. In addition, Lagrangian methods often
have less restrictive conditions on time steps than Eulerian
methods\footnote{In Eulerian methods, the mesh is fixed.}.
When solving PDEs on unstructured meshes
with Lagrangian methods, the nodes move (since they
are treated like particles) and the mesh ``travels''.
A flow-based change to a mesh can cause problems if it
distorts the mesh until the element
quality is too low in some mesh elements. Over enough time, the mesh can
even tangle (i.e. elements begin to overlap).
